---
title: "preprocess"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,message=FALSE, warning=FALSE,results='hide'}
library(ggplot2)
library(rsample)
library(recipes)
library(dplyr)
library(caret)
library(pROC)
library(kernlab)
library(tidyverse)
library(gbm)
library(xgboost)
library(klaR)
library(h2o)
library(ranger)
library(pdp)
```

```{r}
data <- read.csv("movies_with_clusters.csv")[,c(-1,-3:-54,-73)]
dim(data)
str(data)
```

#data preprocess
```{r}
blueprint <- recipe(gross ~ ., data = data) %>% 
  step_nzv(all_predictors()) %>%
  step_log(all_numeric(), base = 10,offset=7) %>% # normalize to resolve numeric feature skewness
  step_center(all_numeric(), -all_outcomes()) %>%
  step_scale(all_numeric(), -all_outcomes())
```

```{r}
prep <- prep(blueprint, training = data)
data<-bake(prep,new_data=data)
```
```{r}
dim(data)
str(data)
```

```{r}
library(PerformanceAnalytics)
chart.Correlation(data[,-4], histogram=TRUE,method="pearson",pch=19) 
```

```{r}
#Regression without clusters
fit_all_nocluster<-lm(gross~avg_like_cnt+avg_com_cnt+avg_share_cnt+avg_star_rating+avg_sen_score+avg_sen_score_2+avg_sen_score_3+pos_rate, data = data)
summary(fit_all_nocluster)
```
If the time of audience behavior is not subdivided, we can see that avg_like_cnt, avg_com_cnt and avg_star_rating has a significant impact on box office revenue. The number of likes, comments and scores without considering the likes and emotion of comments are positively correlated with box office revenue, while other factors are negatively correlated.

```{r}
#Rrgression with special time
fit_all_t123<-lm(gross~avg_like_cnt_t1+avg_like_cnt_t2+avg_like_cnt_t3+avg_com_cnt_t1+avg_com_cnt_t2+avg_com_cnt_t3+avg_share_cnt_t1+avg_share_cnt_t2+avg_share_cnt_t3+avg_star_rating+avg_sen_score+avg_sen_score_2+avg_sen_score_3+pos_rate, data = data)
summary(fit_all_t123)
```
Breaking down the time before, during and after release, we can see that only ratings and scores that do not include the likes and emotions of reviews have a significant correlation with the movie's box office. Among likes, comments and shares, only the amount of shares before and during the release was positively correlated with box office.

```{r}
par(mfrow=c(2,2))#2*2的图形分布
plot(fit_all_t123)
```

The overall effect is ideal
· The residuals are normally distributed and independent of the estimate
· Variance is basically determined
· Two notable outliers appear, but are still within the 0.5 Cook distance

```{r}
coef(fit_all_t123)
confint(fit_all_t123)
```

They're all in the confidence interval.

```{r}
lm_step<-stats::step(fit_all_t123)
summary(lm_step)
```
```{r}
drop1(lm_step)
```
```{r}
#拟合新模型
opt.lm <- lm(gross~avg_like_cnt_t1+avg_like_cnt_t3+avg_star_rating+avg_sen_score+avg_sen_score_3, data = data)
summary(opt.lm) 
```

The number of likes and comments' emotion after the screening is positively correlated with box office.

```{r}
anova(opt.lm,fit_all_t123)
```

Since the test is not significant (P =0.684), it can be concluded that this other predictive variable can be removed without the need to add it to the model. Therefore, the optimal model only needs to contain 5 variables, avg_like_cnt_t1, avg_like_cnt_t3,  avg_star_rating, avg_sen_score, avg_sen_score_3.

```{r}
par(mfrow=c(2,2))#2*2的图形分布
plot(opt.lm)
```

The overall effect is ideal
· The residuals are normally distributed and independent of the estimate
· Variance is basically determined
· Two notable outliers appear, but are still within the 0.5 Cook distance

```{r}
library(PerformanceAnalytics)
set <- as.data.frame(data[,c("gross", "avg_like_cnt_t1", "avg_like_cnt_t3","avg_star_rating","avg_sen_score","avg_sen_score_3")])
car::scatterplotMatrix(set,spread=FALSE,lty.smooth=2,main="Movies")
```

The likes before and after the screening showed a significant positive correlation tilt.

```{r}
library(ggplot2)
library(ggpmisc)

my.formula <- y ~ x

ggplot(data, aes(x =avg_like_cnt_t1+avg_like_cnt_t3+avg_star_rating+avg_sen_score+avg_sen_score_3, y = gross)) +
  geom_smooth(method = "lm", 
              se=FALSE, color="black", 
              formula = my.formula) +
  stat_poly_eq(formula = my.formula, 
               aes(label = paste(..eq.label.., 
                                 ..rr.label.., 
                                 sep = "~~~")), 
               parse = TRUE) +         
  geom_point(size=4,
             alpha=0.7,
             color="#fe654c")+
  coord_cartesian(ylim = c(5,10),
                  xlim = c(0,8))+
  scale_y_continuous(breaks = c(5,10))+
  scale_x_continuous(breaks = c(0,5))+
  theme_bw()+
  geom_smooth(method = "lm",
              color="#558ebd",
              fill="lightgray",
              alpha=.7,
              size=0.8,se=T,
              formula = y~x)+
  theme(panel.grid = element_blank())
```

```{r}
ggplot(data,aes(x=avg_like_cnt_t1,y=gross))+geom_smooth(method='lm')+geom_point()
```

```{r}
ggplot(data,aes(x=avg_like_cnt_t3,y=gross))+geom_smooth(method='lm')+geom_point()
```
```{r}
ggplot(data,aes(x=avg_star_rating,y=gross))+geom_smooth(method='lm')+geom_point()
```
```{r}
ggplot(data,aes(x=avg_sen_score,y=gross))+geom_smooth(method='lm')+geom_point()
```

```{r}
ggplot(data,aes(x=avg_sen_score_3,y=gross))+geom_smooth(method='lm')+geom_point()
```

